---
title: "Question 5: Volatility and GARCH estimates"
documentclass: elsarticle
Thesis_FP: false
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: true
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Vincent Reinshagen
Ref1: Stellenbosch University
Email1: 28736907@sun.ac.za
BottomRFooter: \footnotesize Page \thepage
addtoprule: true
addfootrule: true
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: true
linenumbers: false
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: true
Journal: Journal of Finance
toc: false
numbersections: true
fontsize: 11pt
linestretch: 1.2
link-citations: true
AddTitle: true
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
library(tbl2xts)



# Notice that as you are working in a .Rproj file (I am assuming you are) - the relative paths of your directories start at your specified root.
# This means that when working in a .Rproj file, you never need to use getwd() - it is assumed as your base root automatically.


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->



<!-- The following is a code chunk. It must have its own unique name (after the r), or no name. After the comma follows commands for R which are self-explanatory. By default, the code and messages will not be printed in your pdf, just the output: -->

```{r Figure1,  warning =  FALSE, fig.align = 'center', fig.cap = "Caption Here \\label{Figure1}", fig.ext = 'png', fig.height = 3, fig.width = 6}

pacman::p_load("MTS", "robustbase")
pacman::p_load("tidyverse", "devtools", "rugarch", "rmgarch", 
    "forecast", "tbl2xts", "lubridate", "PerformanceAnalytics", 
    "ggthemes")

cncy <- read_rds("/Users/x/Downloads/28736907_Fin_Metrics/Questions/Question5/data/currencies.rds")
cncy_Carry <- read_rds("/Users/x/Downloads/28736907_Fin_Metrics/Questions/Question5/data/cncy_Carry.rds")
cncy_value <- read_rds("/Users/x/Downloads/28736907_Fin_Metrics/Questions/Question5/data/cncy_value.rds")
cncyIV <- read_rds("/Users/x/Downloads/28736907_Fin_Metrics/Questions/Question5/data/cncyIV.rds")
bbdxy <- read_rds("/Users/x/Downloads/28736907_Fin_Metrics/Questions/Question5/data/bbdxy.rds")

```

The plot displays the 10 most volatile currencies over the observed period, with South Africa's currency (ZAR) consistently ranking among them. Notably, prior to 2002, the ZAR exhibited relatively lower volatility compared to its peers. However, post-2002, it emerges as one of the most volatile currencies in the dataset, frequently remaining near the top of the list in terms of volatility. The plot substantiates the initial statement regarding ZAR's behavior, particularly its performance in high-risk environments and its association with volatility.

```{r}
xts_cncy <- cncy %>% spread(Name, Price) %>% tbl_xts()
index(xts_cncy) <- as.Date(index(xts_cncy))
xts_cncy <- xts_cncy[!weekdays(index(xts_cncy)) %in% c("Saturday", "Sunday"), ]
xts_cncy <- xts_cncy[, !apply(is.na(xts_cncy), 2, any)]



currency_volatility(xts_cncy)
```


The market implied volatility further corroborates the findings from the actual volatility analysis. While the ZAR is not consistently the currency with the highest implied volatility, there are distinct periods where its implied volatility significantly exceeds that of other currencies, sometimes by a substantial margin. This pattern highlights the ZAR's sensitivity to global market dynamics and its heightened vulnerability during periods of elevated risk or uncertainty.

```{r}
xts_IV <- cncyIV %>% spread(Name, Price) %>% tbl_xts() %>% .["1999-03-01/"] 
xts_IV <- xts_IV[, colSums(is.na(xts_IV)) == 0]


currency_volatility(xts_IV)


```


The regression results provide insights into the statement, "The ZAR has generally performed well during periods where G10 currency carry trades have been favourable and currency valuations relatively cheap. Globally, it has been one of the currencies that most benefit during periods where the Dollar is comparatively strong, indicating a risk-on sentiment." However, the findings partially align with the statement and partially contradict it.
The relationship between the ZAR and the G10 carry trade index (Carry_Index_norm) shows a negative coefficient (-0.086), indicating that ZAR tends to weaken when G10 carry trades are favorable. This contradicts the statement's claim that ZAR performs well during such periods. A possible explanation could be that favorable G10 carry trades attract capital toward higher-yielding G10 currencies, making them more competitive against emerging market currencies like the ZAR.
The positive coefficient for the dollar index (Dollar_Index_norm) at 0.844 supports the second part of the statement, which claims that ZAR benefits during periods of dollar strength. This relationship suggests that ZAR appreciates when the dollar strengthens, aligning with risk-on sentiment where emerging markets like South Africa attract investor interest.
Lastly, the negative coefficient for volatility (Volatility_norm) at -0.0346 aligns with the broader implication of the statement that ZAR performs poorly during periods of uncertainty or risk aversion. High volatility reflects greater market uncertainty, which tends to weaken ZAR.

```{r}
ZAR <- xts_cncy %>% xts_tbl() %>% select(date, SouthAfrica_Cncy)
ZAR_IV <- cncyIV %>% spread(Name, Price) %>% select(date, SouthAfrica_IV)

data <- process_data(cncy_Carry, bbdxy, ZAR_IV, ZAR)

model <- lm(ZAR_Rate_norm ~ Carry_Index_norm + Dollar_Index_norm + Volatility_norm, data = data)

regression_summary(model)

```

The plot of normalized variables reinforces the findings from the regression table, and to provide further clarity, the subsequent plot illustrates the rolling correlations.

```{r}
plot_normalized(data)
```

The rolling correlations in the chart highlight the dynamic relationships between the ZAR rate and the predictors over time, which adds nuance to the previous regression-based interpretation. The correlation between ZAR and the carry index (red line) fluctuates significantly, alternating between positive and negative values. This indicates that the relationship is not consistent and that ZAR does not always benefit during favorable carry trade periods, aligning with the earlier regression findings.

In contrast, the dollar index (green line) generally shows a strong and sustained positive correlation with ZAR over time, reinforcing the conclusion that ZAR appreciates during periods of dollar strength, consistent with the statement about risk-on sentiment. The relationship between volatility (blue line) and ZAR is more volatile but tends to hover around a negative correlation, supporting the idea that increased market uncertainty (high volatility) weakens ZAR.

```{r}

plot_rolling_correlations(data, 252)
```


The scatterplots provide additional context to the relationships between the ZAR exchange rate and the predictors. The negative slope in the relationship between ZAR and the carry index (DBHVG10U) indicates that ZAR weakens when G10 carry trade returns are favorable, which is consistent with the regression findings but contradicts the statement that ZAR benefits during such periods. This may reflect a preference for G10 currencies over emerging market currencies like ZAR during favorable carry trade conditions. Conversely, the positive slope between ZAR and the dollar index (BBDXY) reinforces the idea that ZAR appreciates during periods of dollar strength, aligning with the statement’s claim that ZAR benefits during risk-on sentiment when the dollar strengthens. The relationship between ZAR and implied volatility shows a slightly positive slope, which is unexpected given the usual risk-off impact of volatility on emerging market currencies. This weak relationship suggests that volatility might have less direct influence on ZAR or that other factors mitigate its impact. 

```{r}
plots(data)
```







