---
title: "Question 1: Systematic AI Fund"
documentclass: elsarticle
Thesis_FP: false
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: true
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Vincent Reinshagen
Ref1: Stellenbosch University
Email1: 28736907@sun.ac.za
# Author2: John Smith
# Ref2: Some other Institution, Cape Town, South Africa
# Email2: John\@gmail.com
# CommonAffiliation_12: true
# Author3: John Doe
# Email3: Joe\@gmail.com
# CorrespAuthor_1: true
# keywords: Multivariate GARCH \sep Kalman Filter \sep Copula
# JELCodes: L250 \sep L100
# BottomRFooter: \footnotesize Page \thepage
addtoprule: true
addfootrule: true
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: true
linenumbers: false
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: true
Journal: Journal of Finance
toc: false
numbersections: true
fontsize: 11pt
linestretch: 1.2
link-citations: true
AddTitle: true
#abstract: |
  # Abstract to be written here. The abstract should not be too long and should provide the reader with a good understanding what you are writing about. Academic papers are not like novels where you keep the reader in suspense. To be effective in getting others to read your paper, be as open and concise about your findings here as possible. Ideally, upon reading your abstract, the reader should feel he / she must read your paper in entirety.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
library(tbl2xts)

# Notice that as you are working in a .Rproj file (I am assuming you are) - the relative paths of your directories start at your specified root.
# This means that when working in a .Rproj file, you never need to use getwd() - it is assumed as your base root automatically.
#write_rds(Example_data, path = "data/Example_data.rds")

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->




```{r}
ASISA <- read_rds("/Users/x/Downloads/28736907_Fin_Metrics/Questions/Question1/data/ASISA_Rets.rds")
BM <- read_rds("/Users/x/Downloads/28736907_Fin_Metrics/Questions/Question1/data/Capped_SWIX.rds")
AI_Funds <- read_rds("/Users/x/Downloads/28736907_Fin_Metrics/Questions/Question1/data/AI_Max_Fund.rds")
```


```{r}
pacman::p_load("xts", "tbl2xts", "PerformanceAnalytics", "RcppRoll")

AI_xts <- AI_Funds %>% tbl_xts()
ASISA_xts <- ASISA %>% select(-Index, -FoF) %>% spread(Fund, Returns) %>% tbl_xts() 

ASISA_mean <- mean_A(ASISA) 

BM_xts <- BM %>% select(-Tickers) %>% tbl_xts()

merged <- merge.xts(AI_xts, ASISA_mean, BM_xts) %>% na.omit() 
colnames(merged) <- c("AI_Fund", "Managed_Funds", "Benchmark")

```

I will start my analysis using the PerfomanceAnalytics package, to make use of this package, it is necessary to spread the data. Since we also want to compare the AI Fund to managed funds, I created the function mean_A which calculates the returns across all funds for each date. The format of the three datasets now allows to merge them. Furthermore, the columns are renamed for clarity. The merged dataset can then be used to plot a cumulative return chart.

The plot shows, that the AI Fund (black line) shows a notably higher cumulative return compared to the Benchmark (green line) and Managed Funds (red line). The Managed Funds perform consistently below both the Benchmark and AI Fund over time.

```{r}
chart.CumReturns(merged, legend.loc = 1)
```

After calculating cumulative returns to assess overall performance, rolling returns are analyzed to evaluate consistency and resilience over different time periods, addressing potential biases from early outcomes or isolated events. 

This plot aligns with the general conclusions from the previous plot but provides a more granular view of short-term performance trends over time.

While the previous chart highlighted the AI Fund's superior cumulative returns, this chart shows that the AI Fund's rolling 12-month returns are more volatile but still consistently outperform the Benchmark and Managed Funds over longer periods. The AI Fund exhibits higher peaks and lower troughs compared to the others, suggesting higher risk but also higher reward. Managed Funds consistently exhibit lower volatility and returns, staying below the AI Fund and often below the Benchmark.

```{r}
chart.RollingPerformance(merged, 36, legend.loc = 3)
```

This density plot complements the earlier findings: The AI Fund (red) has a broader and flatter distribution, indicating higher variance and a wider range of returns. Its mean is higher than both the Benchmark and Managed Funds, reinforcing its superior performance over time. The Managed Funds (blue) show a narrower distribution, reflecting lower variability in returns. However, its mean is the lowest among the three datasets, confirming its consistent underperformance relative to the AI Fund and the Benchmark.The Benchmark (green) displays a middle ground, with a tighter distribution compared to the AI Fund but slightly wider than the Managed Funds. Its mean return is higher than Managed Funds but below the AI Fund.

```{r}
density_plot(merged, 36)
```

The density plot with variances confirms that the AI Fund, while offering higher returns, also comes with increased risk compared to the other two datasets. Managed Funds provide the most stability but underperform in terms of both returns and risk-adjusted performance.

```{r}
density_plot_var(merged, 36)
```

Rolling plot already shows lowest variance for Managed funds, and highest variance for AI fund
The drawdown chart emphasizes the AI Fund's greater susceptibility to sharp declines, despite its long-term outperformance.

```{r}
DownsideDeviation(merged, 0)
chart.Drawdown(merged, legend.loc = 3)
```

The analysis highlights that the AI Fund consistently outperforms both the Benchmark and Managed Funds in terms of returns, albeit with higher volatility and deeper drawdowns. While Managed Funds offer lower risk and more stability, they underperform in both mean and cumulative returns. The Benchmark provides a moderate balance of risk and performance but cannot match the AI Fund's long-term growth. This suggests the AI Fund is better suited for risk-tolerant investors seeking higher returns, while Managed Funds cater to more conservative strategies.

