---
title: 'Question 3: Portfolio Construction'
documentclass: elsarticle
Thesis_FP: false
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: true
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Vincent Reinshagen
Ref1: Stellenbosch University
Email1: 28736907@sun.ac.za
addtoprule: true
addfootrule: true
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: true
linenumbers: false
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: true
toc: false
numbersections: true
fontsize: 11pt
linestretch: 1.2
link-citations: true
AddTitle: true
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
library(tbl2xts)



# Notice that as you are working in a .Rproj file (I am assuming you are) - the relative paths of your directories start at your specified root.
# This means that when working in a .Rproj file, you never need to use getwd() - it is assumed as your base root automatically.


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->




```{r}
ALSI <- read_rds("/Users/x/Downloads/28736907_Fin_Metrics/Questions/Question3/data/ALSI.rds")
RebDays <- read_rds("/Users/x/Downloads/28736907_Fin_Metrics/Questions/Question3/data/Rebalance_days.rds")
MonZar <- read_rds("/Users/x/Downloads/28736907_Fin_Metrics/Questions/Question3/data/Monthly_zar.rds")
```

```{r}
library(tbl2xts)
library(xts)
```

The plot illustrates the cumulative returns of ALSI and SWIX over time. Although the ALSI exhibits some initial underperformance, it demonstrates a significant recovery and ultimately surpasses the SWIX, achieving notably higher returns in the long run.

```{r}
rtn <- ALSI %>% select(date, Tickers, Return) %>% spread(Tickers, Return) %>% tbl_xts()
weights_ALSI <- weights(ALSI, "J203")
weights_SWIX <- weights(ALSI, "J403")

cum_returns(return_data = rtn, 
                         weights_data1 = weights_ALSI, 
                         weights_data2 = weights_SWIX, 
                         weight_name1 = "ALSI", 
                         weight_name2 = "SWIX")

```

To determine whether capitalization impacts returns and whether it should be considered in further analysis, the rolling performance is examined. The plot, however, does not provide a definitive conclusion, suggesting that there are no significant long-term performance differences across varying capitalizations.

```{r}


ALSI_index_ret <- ALSI_index(ALSI)

library(PerformanceAnalytics)
chart.RollingPerformance(ALSI_index_ret, width = 252, legend.loc = 1)


```

To gain deeper insight into the differences between the ALSI and the SWIX, their sector exposures should be analyzed. The analysis reveals a clear distinction between the two indexes, with the ALSI assigning a significantly higher weight to resources compared to the SWIX.

```{r}
sector_exp(ALSI)

```

Another notable difference lies in stock concentration, with the top 10 stocks holding a significantly higher share in the ALSI compared to the SWIX.

```{r}
stock_concentration(ALSI, 10)

```



The Capped_funds function enables us to observe the impact of varying caps on different funds. The plot indicates that the return difference between ALSI and SWIX widens as caps increase. This suggests that the higher growth in the ALSI is driven by stocks with greater weight, aligning with the higher stock concentration observed in the previous analysis.

```{r}
Capped_funds(
  ALSI = ALSI, 
  RebDays = RebDays, 
  J203_cols = c("J203", "J403"), 
  W_Cap_values = c(0.05, 0.10)
)
```




